full title

### 2020-10-29 paper/pldi21/combined.tex
Added example for checker

We define the \textit{combined analysis} of the abstract interpretation and the
sealed symbolic execution.  In the combined analysis, we use the powerset of
symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
view transition as follows:
\[
  \begin{array}{l}
    \combviewtrans{\view}{\view'}(\combelem) =\\
    \qquad \{
      \symbst' \mid \symbst \in S \wedge
      \symbst \symbtrans \symbst' \wedge
      \saconverter(\symbst') = (\view', \_)
    \}\\
    \qquad \cup \left\{
    \begin{array}{ll}
      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
      & \text{if} \; D \neq \varnothing\\
      \varnothing & \text{otherwise}\\
    \end{array}
    \right.
  \end{array}
\]
where $S = \combelem\mid_{\checker}$ and $D =
\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
denotes the element-wise extended function of a function $f$.  We could
configure when the sealed symbolic execution or the abstract interpretation is
performed based on the definition of the $\checker$ function and its negation
$\neg\checker$.  The combined analysis performs one-step symbolic transition for
each symbolic state that passes the filter $\checker$. On the other hand, it
converts remaining symbolic states to the corresponding abstract states, merges
them into a single abstract state, and performs the abstract one-step execution
for the abstract state.

@@

For the soundness and the termination of the combined analysis, the filter
$\checker$ in the extended view transition should satisfy the following
condition:
\begin{theorem}
  The combined analysis has sound analysis result and terminates in a finite
  time if its abstract semantics is sound and $\checker$ satisfies the following
  condition:
  \[
    \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
    1 < k \leq N
  \]
  where $N$ is a pre-defined maximum length of the sealed symbolic execution.
\end{theorem}
\inred{We prove that any combined analysis defined with the extended view
transition satisfying the above condition always has sound analysis result and
terminates in a finite time. Because of the page limitation, we omit the
proof in this paper and include it in a companion report.}

>>>>

We define the \textit{combined analysis} of the abstract interpretation and the
sealed symbolic execution.  In the combined analysis, we use the powerset of
symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
view transition as follows:
\[
  \begin{array}{l}
    \combviewtrans{\view}{\view'}(\combelem) =\\
    \qquad \{
      \symbst' \mid \symbst \in S \wedge
      \symbst \symbtrans \symbst' \wedge
      \saconverter(\symbst') = (\view', \_)
    \}\\
    \qquad \cup \left\{
    \begin{array}{ll}
      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
      & \text{if} \; D \neq \varnothing\\
      \varnothing & \text{otherwise}\\
    \end{array}
    \right.
  \end{array}
\]
where $S = \combelem\mid_{\checker}$ and $D =
\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
denotes the element-wise extended function of a function $f$.  The combined
analysis performs one-step symbolic transition for each symbolic state that
passes the filter $\checker$. On the other hand, it converts remaining symbolic
states to the corresponding abstract states, merges them into a single abstract
state, and performs the abstract one-step execution for the abstract state.

@@

We could configure when the sealed symbolic execution or the abstract
interpretation is performed based on the definition of the $\checker$ function
and its negation $\neg\checker$.  For example, we could define the $\checker$
that passes only function entry, call, and exit points to perform conversions in
a function level.  However, for the soundness and the termination of the
combined analysis, it should satisfy the following condition:
\begin{theorem}
  The combined analysis has sound analysis result and terminates in a finite
  time if its abstract semantics is sound and $\checker$ satisfies the following
  condition:
  \[
    \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
    1 < k \leq N
  \]
  where $N$ is a pre-defined maximum length of the sealed symbolic execution.
\end{theorem}
\inred{We prove that any combined analysis defined with the extended view
transition satisfying the above condition always has sound analysis result and
terminates in a finite time. Because of the page limitation, we omit the
proof in this paper and include it in a companion report.}
